---
title: "Homework3"
author: "Evelin Reyes"
date: "10/16/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Homework #3
# Q1 Suppose we have a dataset A (see code below) where each column represents multiple 
# measures of nitrogen concentration in a particular lake.
# We want to get the average value for each lake. Do this in two ways: a for loop and a vectorized function colMeans().

```{r}
set.seed(12) # to be reproducible
A = matrix(data = runif(n = 1:500), nrow = 50, ncol = 10)
colnames(A) = paste("lake", 1:10, sep = "_")
#Answer 1
for(i in 1:10){
  M = mean(A[,i])
  print (M)
}

colMeans(A)
```


## Q2 (2 points) From the for loop lecture,
#we see the following example of using apply():
```{r}
x = array(1:27, dim = c(3, 3, 3))
apply(X = x, MARGIN = c(1, 2), 
      FUN = paste, collapse = ", ")

# Answer 2
y = array(0, dim = c(3, 3, 3))
for (i in 1:3){
  for (j in 1:3) {
    for (k in 1:3) {
      y[i,j,] = paste(x[i,j,],collapse = ",")
    }
    
  }
}
y
```

##Q3 (2 points) The Fibonacci Sequence is the series of numbers that the next number is the sum of the previous two numbers:
# 0, 1, 1, 2, 3, 5, 8 … Use a for loop to get the first 30 numbers of the Fibonacci Sequence. 
#This question should demonstrate the need for loops because there is no easy way to use vectorized functions in this case.

```{r}
#Answer 3
N=numeric()
for (i in 1:30) {
  N[1] = 0
  N[2] = 1
  N[i+2] = N[i]+N[i+1]
}
N
```

##Q4 (2 points) In the example data below, extract those ranking numbers with regular expression. 
#The results should have the number(s) and .
#if it follows after the numbers immediately (i.e., 1., 12., 105., 105.3, etc.). Remove empty strings from the final results. You should get 107 strings for your results.

```{r}
top105 = readLines("http://www.textfiles.com/music/ktop100.txt")
top105 = top105[-c(64, 65)] # missing No. 54 and 55
top105
#Answer 4

pattern <- "^[0-9]*\\.*[0-9]\\."
library("stringr")
A = str_extract(top105,pattern)
A
B = grep("^[0-9]*\\.*[0-9]\\.*[0-9]", A, value = TRUE)
B
```

##Q5 (2 points) For the vector with length of 107 you got from question 4, remove all trailing .. (hint: ?sub). 
#Then convert it to a numeric vector and find out which numbers have duplications (i.e., a tie in ranking). Don’t count by eyes, use R to find it out (hint: table(), sort(); or duplicated(), which(), [ subsetting; there are more than one way to do so).

```{r}
#Answer 5
C = as.numeric(B)
is.numeric(C)
D <- gregexpr(pattern = "(\\d{1,3})", text = C)
E = regmatches(C,D)
C[duplicated(C, incomparables = FALSE)]
```

