---
title: "hw_02"
author: "Evelin Reyes"
date: "10/5/2021"
output:
  pdf_document: default
  html_document: default
---


# HOMEWORK 2 

## Q1 (2 points) Fix each of the following common data frame subsetting errors:

```{r}
mtcars[mtcars$cyl < 6,]
x <- mtcars[-c(1:3), ]
x <- mtcars[mtcars$cyl == 8, ]
x <- mtcars[mtcars$cyl == 4 | mtcars$cyl == 6, ]
```

## Q2 (1 point) Why does the following code generated five missing values?

Using "NA" command on dataframe X tells R to display "NA" for each of the five values that you specified when first creating the X dataframe.

## Q3 (2 points) Why does mtcars[1:15] return an error? How does it differ from mtcars[1:15, ]?

Running mtcars[1:15] gives an error because the code does not specify which column you want R to pull the data from.

## Q4 (2 points) Explain how does the following code work.

The first line of code creates a 3x3 matrix with missing values for positions 4, 8, and 9 the next second line of code assigned the value of 0 for any missing values in data matrix X

## Q5 (3 points) Load the Car Road Tests dataset (in R, run data("mtcars"), ?mtcars), then add a new column named as mpg_2 for the mtcars data frame.

```{r}
mpg2<- 
  ifelse(mtcars$mpg < 16, "low", 
         ifelse(mtcars$mpg < 21, "Low_intermediate",
                ifelse(mtcars$mpg < 26, "Intermediate_high", "High")))

mtcars$mpg_2 = mpg2
mtcars
```

