---
title: "Hmw_06"
author: "Evelin Reyes"
date: "11/8/2021"
output: html_document
---

## Q1
```{r}
d = data.frame(x = c(110.5, 105.4, 118.1, 104.5, 93.6, 84.1, 77.8, 75.6),
y = c(5.755, 5.939, 6.010, 6.545, 6.730, 6.750, 6.899, 7.862))
plot(d$x, d$y, xlab = "plant height", ylab = "grain yield")
```

#### Answer a
```{r}
cor(d$x, d$y)
fit_d = lm(y ~ x, data = d)
summary(fit_d)

#beta 0
coef(fit_d)[1]

# beta 1  Units??
coef(fit_d)["x"]

plot(d$x, d$y, pch=16,
     xlab = "Plant Height",
     ylab = "Grain Yield",
     main = "Scatterplot of Rice Plant Growth  vs Grain Yield") +
abline(coefficients(fit_d), lwd = 2, lty = 2,
       col = "red")
## the estimate tells us that the grain yield will decrease as the plant gets taller. The regression line indicates that yield will likely fall below 6.0 once plant height is more than about 105
```

#### Answer b
```{r}
anova(fit_d)
summary(fit_d)
## Both the F test and T test gave a p-value of less than 5%, allowing us to reject a null hypothesis of the slope value = 0
```

### Answer C
```{r}
qt(0.05/2, 8-2)
# 95% of the time that the confidence interval is calculate it will overlap with the true value of the slope.
confint(fit_d)
```

#### Answer d
```{r}
{plot(d$x,d$y)
abline(fit_d)}

{y=plot(resid(fit_d), x=1:8)
abline(fit_d)}
### resid(fit_d) gives me the actual value of the residuals
### abline(fit_d) plots the slope
{par(mfrow=c(2,2)) ## plotting the residuals vs fitted lines. 
plot(fit_d)}
```

### Answer e
```{r}
SSE<-sum((fitted(fit_d) - d$y)^2)

ev<-SSE/(8-2)
sum(fit_d$residuals**2)

ev1<-anova(fit_d)
ev1<-ev1$`Mean Sq`[2]
```

### Answer f
```{r}
est<-predict(fit_d, newdata = data.frame(x = 100), interval = "confidence")
####int[1] its how much the 100 things is gonna yield, int[2] is the lower bound of the ci and int[3] is the upper bound
        
```

### Answer g
```{r}
pred<-predict(fit_d, newdata = data.frame(x = 100), interval = "prediction")
####int[1] its how much the 100 things is gonna yield, int[2] is the lower bound of the ci and int[3] is the upper bound
        
```

### Answer h
```{r}
sumar<-summary(fit_d)
sumar$r.squared
##### This means how well the model fits the data
```

## Q2
## 2a answer
```{r}
x2 = c(1, 2, 3, 4, 5, 6, 7, 8, 9)
y2 = c(-2.08, -0.72, 0.28, 0.92, 1.20, 1.12, 0.68, -0.12, -1.28)
plot(x = x2, y = y2)
```

## 2b answer
```{r}
modelo<-lm(y2~x2)
rr<-resid(modelo)
plot(x = rr, y = y2)

```

## 2c answer
```{r}
plot(x = x2, y = rr)
```

## 2d answer
```{r}
modelo$fitted.values
plot(x = rr, y = modelo$fitted.values)
```

## 2e answer
### Yes, there is a meaningfull difference between plot c and d. In ### plot d, rr value maximises when fitted value is at zero. In plot ### c, rr value does not respond this way, instead maximizing aroudn five.
### Plot b is a better indication of lack of fit, because the points are close fit to a line of regression. 
